### 2022-05-17 manuscript.Rmd
Update statements

The datasets generated and analyzed during the current study are available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

The analysis code for the current study is available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public link upon acceptance.

@@

>>>>

The datasets generated and analyzed during the current study are available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public DOI link upon publication.

@@

The analysis code for the current study is available in an Open Science Framework repository, [https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8](https://osf.io/k3wdg/?view_only=06a4a0ac3d5f4681baab11751c1498b8) [@enge2022a]. This link is intended for peer review only and will be replaced with a public DOI link upon publication.

@@

- Cite all studies included in the MA
- Change abstract and main headings
- Move figures and tables from the methods to the supplement
